%ACM DOCUMENT
\documentclass[acmtoms]{acmtrans2m}

\usepackage[utf8]{inputenc}
%PACKAGES FOR MATH SYMBOLS
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

%PACKAGE FOR PICTURES
\usepackage{graphicx}

%PACKAGES FOR ALGORITHMS
\usepackage{algorithmicx}
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{algc}
\newcommand{\New}{\textbf{new}}

\acmVolume{1}
\acmNumber{1}
\acmYear{12}
\acmMonth{July}

% New commands
\newcommand{\DP}[2]{\displaystyle\frac{\partial #1}{\partial #2}}
\newcommand{\ds}{\displaystyle}
\newcommand{\bi}[1]{\boldsymbol{\mathit{#1}}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\bv}[1]{\mathbf{#1}}
\renewcommand{\b}[1]{\boldsymbol{\mathit{#1}}}

%HEADER
\markboth{M. Costa et al.}{Design and Implementation of the Three-Dimensional Autonomous Leaves Graph}

%TITLE
\title{ Design and Implementation of the Three-Dimensional Autonomous Leaves Graph Data Structure}

%AUTHORS
% \author
% {
%     MAYCON DA COSTA$^{\textrm{\,a}}$, DENISE BURGARELLI$^{\textrm{\,b}}$,
%     RODNEY JOSU\'E BIEZUNER$^{\textrm{\,b}}$ RAFAEL SACHETTO OLIVEIRA \and WAGNER MEIRA
%     JR.$^{\textrm{\,a}}$, Universidade Federal de Minas Gerais\\
%     RODRIGO WEBER DOS SANTOS, Universidade Federal de Juiz de Fora
%
% }
 \author
 {
     MAYCON DA COSTA, DENISE BURGARELLI,
     RODNEY JOSU\'E BIEZUNER, RAFAEL SACHETTO OLIVEIRA and WAGNER MEIRA
     JR., Universidade Federal de Minas Gerais \\
     RODRIGO WEBER DOS SANTOS, Universidade Federal de Juiz de Fora
 }
%CATEGORY
\category{E.1}{Data Structures}{Graphs and networks}

%TERMS OF THE ARTICLE
\terms{Algorithms, Design}

%KEYWORDS
\keywords{adaptive mesh refinement, ALG data structure, three-dimensional domains, space filling curve}

%DOCUMENT
\begin{document}

        \begin{bottomstuff}
        This work was partially funded by CNPq, Capes, Fapemig and InWeb.\\
        Rafael Sachetto Oliveira is also affiliated with Universidade Federal de
        São João del Rei.\\
        Authors' addresses: D. Burgarelli and R. J. Biezuner,
        Departamento de Matem\'atica, ICEx, Universidade Federal de Minas  Gerais, Av. Ant\^onio Carlos 6627, Pampulha,
        CEP 30161-970, Belo Horizonte, MG, Brazil. emails: burgarelli@ufmg.br, rodney@mat.ufmg.br.
        R.S. Oliveira, Departamento de Ciência da Computação,
        Universidade Federal de São João del-Rei, CTAN,
        Prédio dos Cursos de Ciência da Computação e Zootecnia, 3 andar, Av. Visconde do Rio Preto,
        s/n, Colônia do Bengo, São João del-Rei, MG, Brazil, CEP 36301-360. email:
        sachetto@ufsj.edu.br. W. Meira Jr. and M. Costa, Departamento de Ci\^encia da Computa\c c\~ao, ICEx,
        Universidade Federal de Minas Gerais, Av. Ant\^onio Carlos 6627,
        Pampulha, CEP 31270-010, Belo Horizonte, MG, Brazil. emails:
        mayconufmg@gmail.com , meira@dcc.ufmg.br. Rodrigo Weber dos Santos,
        Universidade Federal de Juiz de Fora, Instituto de Ciências Exatas - Prédio
        MMC - Campus Universitário, Juiz de Fora, MG, Brazil, CEP: 36036-330.
        email: rodrigo.weber@ufjf.edu.br.
        \end{bottomstuff}

%     %AUTHOR'S ADDRESSES
%     \begin{bottomstuff}
%     Author's addresses: \newline
%     $^{\rm a}$ Departamento de Ci\^encia da Computa\c c\~ao, ICEx,
%     Universidade Federal de Minas Gerais, Av. Ant\^onio Carlos 6627,
%     Pampulha, CEP 31270-010, Belo Horizonte, MG, Brazil. E-mails: \linebreak mayconufmg@gmail.com (M. Costa),
%     meira@dcc.ufmg.br (W. Meira Jr.)
%     \newline
%
%     $^{\rm b}$ Departamento de Matem\'atica, ICEx, Universidade
%     Federal de Minas  Gerais, Av. Ant\^onio Carlos 6627, Pampulha,
%     CP 702, CEP 30161-970, Belo Horizonte, MG, Brazil. E-mails: burgarelli@ufmg.br (D. Burgarelli),
%     rodney@mat.ufmg.br (R. J. Biezuner). \newline
%     \end{bottomstuff}

    %ABSTRACT
    \begin{abstract}
    Autonomous Leaves Graph (ALG), a dynamic space-time data
    structure designed to minimize the computational effort of refinement and
    derefinement operations and to allow flexibility in the levels of refinement
    of adjacent regions in space adaptive meshes, was introduced in
    \cite{Burgarelli1998} and implemented for two-dimensional domains. Its
    storage requirements and computational cost compare competitively with other
    mesh refinement schemes based on hierarchical trees. Here an algorithm for
    implementing this scheme for time-evolving three-dimensional spatial domains
    (ALG-3D) is given in full detail.
    \end{abstract}

    \maketitle

    %SECTIONS
    \input{introduction}
    \input{dataStructure}
    \input{refinement}
    \input{derefinement}
    \include{hilbertCurve}
    \include{application}
    %\input{bibliography}
    \bibliographystyle{acmtrans}
    \bibliography{bibliography}

\end{document}
