\begin{thebibliography}{99}

\bibitem[Burgarellio 1998]{Burgarelli1998} BURGARELLI, D. \textit{Modelagem computacional e
simula\c c\~ao num\'erica adaptativa de equa\c c\~oes diferenciais
parciais evolutivas aplicadas a um problema termoac\'ustico}, Ph.D. thesis, PUC-Rio, Rio de Janeiro, Brasil, (1998). (in
Portuguese)

\bibitem[Burgarelli et al. 2006]{Burgarellietal2006}BURGARELLI, D., KISCHINHEVSKY, M. and BIEZUNER, R. J.,
A new adaptive mesh refinement strategy for numerically solving
evolutionary PDE's, \textit{Journal of Computational and Applied
Mathematics} \textbf{196} (2006) 115--131.


\bibitem[Gamezo et al. 2005a]{Gamezoetal2005a}  GAMEZO, V. N.,  KHOKHLOV, A. M. and ORAN, E.S.,
Three-dimensional delayed-detonation model of type Ia supernovae, \textit{The Astrophysical Journal} \textbf{623} (2005) 337-346.


\bibitem[Gamezo et all. 2005b]{Gamezoetal2005b}  GAMEZO, V. N., ORAN , E. S. and   KHOKHLOV, A. M.,
Three-dimensional reactive shock bifurcations, \textit{Proceedings of the Combustion Institute .} \textbf{30} (2005) 1841-1847.


\bibitem[Ji et all. 2008]{Jietal2008}  JI, H., LIEN, F. and   YEE, E.,
A robust and efficient hybrid cut-cell/ghost-cell method with adaptive mesh refinement for moving boundaries on irregular domains, \textit{Comput. methods Appl. Mech. Engrg.} \textbf{198} (2008) 432-448.


\bibitem[Penner et all. 2007]{Penneretal2007}  PENNER, J. E., ANDRONOVA, N.,  OEHMKE,R.C., BROWN,J., STOUT, Q.F., JABLONOWSKI, C., VAN LEER, B., POWELL, K.G. and  HERZOG, M.,
Three Dimensional adaptive mesh refinement on a spherical shell for atmospheric  models with lagrangian coordinates, \textit{Journal of Physics : Conference Series .} \textbf{78} (2007) 1-5.



\bibitem[Tavakoli 2006]{tavakoli2006} TAVAKOLI, R.,
CartGen: Robust, efficient and easy to implement uniform/octree/embedded boundary Cartesin grid generator, \textit{International Journal for Numerical Methods in Fluids} \textbf{57} (2008) 1753--1770.



\end{thebibliography}
